Covid-19 A Spatio-Temporal Investigation.

### 2021-01-11 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The spatial method was calculated by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal Poisson scan statistic, proposed by Kulldorff $\!\!^5$ to identify emerging or "alive" *clusters* in space and time.(later i'll add a few more things regarding two other studies i've found)

@@

 The use of a spatio-temporal scan statistic is useful to identify emerging *clusters*, since the purely spatial scan statistic has a few limitations as it's pointed by Kulldorff (2001, p. 66), by conducting a purely spatial analysis for a long period of time

  (2001, p. 66) se fizermos uma análise puramente especial por um período extensivo de tempo, nós temos pouco poder para detectar *clusters* emergentes, a solução portanto seria usar uma estatística de scan espaço-temporal.

## Resultados

@@

>>>>

 The spatial method was calculated by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal Poisson scan statistic, proposed by Kulldorff $\!\!^5$ to identify emerging or "alive" *clusters* in space and time.

@@

 Spatio-temporal scan statistics are useful to identify emerging *clusters*, since purely spatial scan statistics have a few limitations as it's pointed by Kulldorff (2001, p. 66), there is little power to detect emerging *clusters* when conducting a purely spatial analysis for a long period of time, therefore the solution would be to use a spatio-temporal scan statistic.

## Results

@@

(later i'll add a few more things regarding two other studies i've found)
